Topological Equivariance Artist Model

### 2021-03-11 paper/paper.tex
what even is an intro?

%% the only exception to this rule is the \firstsection command
\firstsection{Introduction}
\maketitle
The aim of this work is to rearchitecture Matplotlib to take advantage of developments in software design, data structures, and visualization, 
to improve consistency, reusability, and discoverability, so that domain specific tool developers can build structure preserving visualization tools. We present a visualization model that formalizes constraints on componenents of a visualization in terms of equivaraiance, continuity, and composibility.

>>>>

%% the only exception to this rule is the \firstsection command
\firstsection{Introduction}
\maketitle
The aim of this work is to rearchitecture Matplotlib to take advantage of developments in software design, data structures, and visualization, 
to improve consistency, reusability, and discoverability, so that domain specific tool developers can build structure preserving visualization tools. To enable this rearchitecture, we first present a visualization model that formalizes the structure that a visualization preserves in terms of 
\begin{enumerate}
  \item equivaraiance of data and visual properties
  \item continuity of data and the graphic
  \item composibility of components developed in ths model
\end{enumerate}
